Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-13 paper/paper.tex
More text in proofs section
changed figure 1

\begin{figure}
    \begin{center}
        \begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm,node distance=10mm,fill=black}]
            \node[fill=uofgcobalt] (a) {};
            \node (a1) [below left of = a] {};
            \node (b1) [below right of = a] {};
            \node (aa) [below right of = a1] {};

            \node (a2) [below left of = aa,node distance=13mm,xshift=2mm] {};
            \node (aa2) [above left of = a2,node distance=13mm,xshift=-2mm] {};
            \node (ab2) [below left of = a2,node distance=13mm,xshift=-2mm] {};
            \node (ac2) [fill=gray!50,above left of = ab2,node distance=13mm,xshift=-2mm] {};
            \node (b2) [below right of = aa,node distance=13mm,xshift=-2mm] {};
            \node (ba2) [above right of = b2,node distance=13mm,xshift=2mm] {};
            \node (bb2) [below right of = b2,node distance=13mm,xshift=2mm] {};
            \node (bc2) [fill=gray!50,above right of = bb2,node distance=13mm,xshift=2mm] {};

            \node (aaa) [below of =aa, node distance=20mm] {};

            \path[dotted] (a) edge (a1) edge (b1);
            \path (aa) edge (a1) edge (b1) edge (a2) edge (b2)
                (a1) edge (b1)
                (aaa) edge (a2) edge (b2)
                (a2) edge (aa2) edge (ab2)
                (b2) edge (ba2) edge (bb2);
            \path[color=gray!50] (ac2) edge (ab2) edge (aa2)
                (bc2) edge (bb2) edge (ba2);

            \node [cross] {};
        \end{tikzpicture}
        \caption{Example of  ``as much of the pattern'' as possible.}
        \label{fig:subgraphexample}
    \end{center}
\end{figure}
\subsection{Definitions and Notations}

@@

If we remove up to $k$ vertices from the neighbourhood of $p$, it will impact the intersection of the neighbourhoods of $p$ and $q$, and by Proposition~\ref{prop:deg}, as $p\lessmap{k}t$
\[
\left| \N(p)\cap \N(q)\right| - k \leq \deg(p) - k \leq \deg(t).
\]
As $\left|\N(p)\cap \N(q)\right|\leq \deg(p) \leq \left|\N(t)\cap \N(u)\right|\leq \deg(t)$, we have
\[
\left|\N(p)\cap \N(q)\right| - k \leq \deg(p) - k\leq \left|\N(t)\cap \N(u)\right|\leq \deg(t)
\]
which is
\[
\paths(p, q, 2) - k \leq \paths(t, u, 2). \qedhere
\]
\end{proof}

>>>>

\begin{figure}
    \begin{center}
        \begin{tikzpicture}[scale=0.6]%[every node/.style={circle, inner sep=0.5mm,node
            %distance=10mm,fill=black}, scale=0.2]

            \begin{scope}[xshift=-1cm, yshift=-3cm, color=black]
            \node at (0, -0.5) {$P$};
            \node [fill, circle, inner sep=1.5pt] (a) at (0,0) {};
            \node [fill, circle, inner sep=1.5pt] (b) at (-1,1) {};
            \node [fill, circle, inner sep=1.5pt] (c) at (0,1) {};
            \node [fill, circle, inner sep=1.5pt] (d) at (1,1) {};
            \node [fill, circle, inner sep=1.5pt] (e) at (0,2) {};

            \path[solid] (a) edge (b) edge (c) edge (d)
                (e) edge (b) edge (c) edge (d);
            % \node (a2) [below left of = aa,node distance=13mm,xshift=2mm] {};
            % \node (aa2) [above left of = a2,node distance=13mm,xshift=-2mm] {};
            % \node (ab2) [below left of = a2,node distance=13mm,xshift=-2mm] {};
            % \node (ac2) [fill=gray!50,above left of = ab2,node distance=13mm,xshift=-2mm] {};
            % \node (b2) [below right of = aa,node distance=13mm,xshift=-2mm] {};
            % \node (ba2) [above right of = b2,node distance=13mm,xshift=2mm] {};
            % \node (bb2) [below right of = b2,node distance=13mm,xshift=2mm] {};
            % \node (bc2) [fill=gray!50,above right of = bb2,node distance=13mm,xshift=2mm] {};

            % \node (aaa) [below of =aa, node distance=20mm] {};
            %
            % \path[dotted] (a) edge (a1) edge (b1);
            % \path (aa) edge (a1) edge (b1) edge (a2) edge (b2)
            %     (a1) edge (b1)
            %     (aaa) edge (a2) edge (b2)
            %     (a2) edge (aa2) edge (ab2)
            %     (b2) edge (ba2) edge (bb2);
            % \path[color=gray!50] (ac2) edge (ab2) edge (aa2)
            %     (bc2) edge (bb2) edge (ba2);
            %
            % \node [cross] {};
            \end{scope}

            \begin{scope}[xshift=2cm, yshift=-3cm, color=black]
            \node at (0, -0.5) {$T$};
            \node [fill, circle, inner sep=1.5pt] (a) at (0,0) {};
            \node [fill, circle, inner sep=1.5pt] (b) at (-1,1) {};
            \node [fill, circle, inner sep=1.5pt] (c) at (1,2) {};
            \node [fill, circle, inner sep=1.5pt] (d) at (1,1) {};
            \node [fill, circle, inner sep=1.5pt] (e) at (0,2) {};
            \node [fill, circle, inner sep=1.5pt] (f) at (1,0) {};
            \node [fill, circle, inner sep=1.5pt] (g) at (2,0) {};
            \node [fill, circle, inner sep=1.5pt] (h) at (2,2) {};

            \path[solid] (a) edge (b) edge (d)
                (e) edge (b) edge (d)
                (d) edge (c) edge (f)
                (c) edge (h)
                (f) edge (g);

            % \node (a2) [below left of = aa,node distance=13mm,xshift=2mm] {};
            % \node (aa2) [above left of = a2,node distance=13mm,xshift=-2mm] {};
            % \node (ab2) [below left of = a2,node distance=13mm,xshift=-2mm] {};
            % \node (ac2) [fill=gray!50,above left of = ab2,node distance=13mm,xshift=-2mm] {};
            % \node (b2) [below right of = aa,node distance=13mm,xshift=-2mm] {};
            % \node (ba2) [above right of = b2,node distance=13mm,xshift=2mm] {};
            % \node (bb2) [below right of = b2,node distance=13mm,xshift=2mm] {};
            % \node (bc2) [fill=gray!50,above right of = bb2,node distance=13mm,xshift=2mm] {};

            % \node (aaa) [below of =aa, node distance=20mm] {};
            %
            % \path[dotted] (a) edge (a1) edge (b1);
            % \path (aa) edge (a1) edge (b1) edge (a2) edge (b2)
            %     (a1) edge (b1)
            %     (aaa) edge (a2) edge (b2)
            %     (a2) edge (aa2) edge (ab2)
            %     (b2) edge (ba2) edge (bb2);
            % \path[color=gray!50] (ac2) edge (ab2) edge (aa2)
            %     (bc2) edge (bb2) edge (ba2);
            %
            % \node [cross] {};
            \end{scope}

        \end{tikzpicture}
        \caption{Notice that $P$ would be isormorphic to a subgraph of $T$ if the middle vertex in the diamond is removed.}
        \label{fig:subgraphexample}
    \end{center}
\end{figure}
\subsection{Definitions and Notations}

@@

If we remove up to $k$ vertices from the neighbourhood of $p$, it will impact the intersection of the neighbourhoods of $p$ and $q$, and by Proposition~\ref{prop:deg}, as $p\lessmap{k}t$
\[
\left| \N(p)\cap \N(q)\right| - k \leq \deg(p) - k \leq \deg(t).
\]
As $\left|\N(p)\cap \N(q)\right|\leq \deg(p) \leq \left|\N(t)\cap \N(u)\right|\leq \deg(t)$, we have
\begin{align*}
\left|\N(p)\cap \N(q)\right| - k & \leq \deg(p) - k\leq \\
 &\leq \left|\N(t)\cap \N(u)\right|\leq \deg(t)
\end{align*}
which is
\[
\paths(p, q, 2) - k \leq \paths(t, u, 2). \qedhere
\]
\end{proof}
